Polyglots: Crossing Origins by Crossing Formats

### 2013-08-26 main.tex
Fixed images, bad breaks and overflows

\paragraph{Overview}
The paper is organized as follows. 
%
Section~\ref{sec:cross} explains the concept of crossing origins by
crossing formats, identifies necessary ingredients, and provides
attack scenarios.
%
Section~\ref{sec:vuln} focuses on the PDF format and describes
concrete vulnerabilities and attacks.
%
Section~\ref{sec:eval} evaluates the current practice in client/server
content filtering and PDF readers and report on vulnerabilities in the
top 100 Alexa web sites.
%
Section~\ref{sec:mit} suggests mitigation for servers, clients, and
PDF readers.
%
Section~\ref{sec:related} discusses the related work.
%
Section~\ref{sec:conc} concludes and outlines future work.

@@

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{scenario.png}
  \caption{Overview of the scenario}
  \label{fig:scenario}
\end{figure}

@@

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{injection-scenario.png}
  \caption{Syntax injection scenario}
  \label{fig:injection-scenario}
\end{figure}

@@

\paragraph{Scenario}
The content smuggling scenario proceeds as illustrated in Figure~\ref{fig:smuggling-scenario}.
Similarly to the previous scenarios, the victim is an authenticated user of a targeted vulnerable web site, \emph{vulnerable.com}. 
To give more context to the scenario, \emph{vulnerable.com} can be a cloud storage service. 
The target is infiltrated by the attacker (1), who uploads a polyglot to the web site. 
The polyglot is verified to be benign under the assumption that it belongs an allowed file type.
%The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
While still authenticated to \emph{vulnerable.com}, 
the victim visits the attackers web site, \emph{attacker.com} (2).
The \emph{attacker.com} site embeds the polyglot from \emph{vulnerable.com} (3), which is served as the benign type, but 
coerced to be interpreted as the malicious content type by the plug-in (4). 
The malicious format of the embedded 
polyglot is activated and a possible payload is to extract all the files stored in the victims account.

@@

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{smuggling-scenario.png}
  \caption{Content smuggling scenario}
  \label{fig:smuggling-scenario}
\end{figure}

@@

\paragraph{PDF as the malicious format}
As detailed in the content smuggling scenario in Section~\ref{sec:smuggling}, the 
attacker uploads the PDF polyglot to a vulnerable content hosting service. 
A server-side verification process will base its verification on the benign formats 
it expects to receive. The polyglot is designed to verify correctly as the benign format,
and the verification is likely to miss the malicious PDF components, as it is unaware of the alternate interpretation of the content.

@@

Listing~\ref{lst:xml-pdf} contains an example PDF document that uses XML external 
entities. Note that the one-way method \emph{getURL} is used to communicate the 
information back to the attacker. Given the compact size of the example, it is useful for the syntax 
injection scenario in Section~\ref{sec:injection}, which require injection of 
small syntax fragments.

@@

\paragraph{Content smuggling}
\label{sec:smuggling-mitigation}
The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
on hosting user-supplied content, is to serve the content from a sandboxed origin that is 
completely separate, as per SOP, and isolated from the sensitive services. 
These best-practices successfully prevents content smuggling 
attacks, as the restrictions of the SOP prevents the content from accessing any sensitive 
resources in the origin of the web service.

>>>>

\vfill\eject
\paragraph{Overview}
The paper is organized as follows. 
%
Section~\ref{sec:cross} explains the concept of crossing origins by
crossing formats, identifies necessary ingredients, and provides
attack scenarios.
%
Section~\ref{sec:vuln} focuses on the PDF format and describes
concrete vulnerabilities and attacks.
%
Section~\ref{sec:eval} evaluates the current practice in client/server
content filtering and PDF readers and report on vulnerabilities in the
top 100 Alexa web sites.
%
Section~\ref{sec:mit} suggests mitigation for servers, clients, and
PDF readers.
%
Section~\ref{sec:related} discusses the related work.
%
Section~\ref{sec:conc} concludes and outlines future work.

@@

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{scenario.pdf}
  \caption{Overview of the scenario}
  \label{fig:scenario}
\end{figure}

@@

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{injection-scenario.pdf}
  \caption{Syntax injection scenario}
  \label{fig:injection-scenario}
\end{figure}

@@

\paragraph{Scenario}
The content smuggling scenario proceeds as illustrated in Figure~\ref{fig:scenario}.
Similarly to the previous scenarios, the victim is an authenticated user of a targeted vulnerable web site, \emph{vulnerable.com}. 
To give more context to the scenario, \emph{vulnerable.com} can be a cloud storage service. 
The target is infiltrated by the attacker (1), who uploads a polyglot to the web site. 
The polyglot is verified to be benign under the assumption that it belongs an allowed file type.
%The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
While still authenticated to \emph{vulnerable.com}, 
the victim visits the attackers web site, \emph{attacker.com} (2).
The \emph{attacker.com} site embeds the polyglot from \emph{vulnerable.com} (3), which is served as the benign type, but 
coerced to be interpreted as the malicious content type by the plug-in (4). 
The malicious format of the embedded 
polyglot is activated and a possible payload is to extract all the files stored in the victims account.

@@

%\begin{figure}[t]
%  \center
%  \includegraphics[width=0.49\textwidth]{smuggling-scenario.png}
%  \caption{Content smuggling scenario}
%  \label{fig:smuggling-scenario}
%\end{figure}

@@

\paragraph{PDF as the malicious format}
In the content smuggling scenario in Section~\ref{sec:smuggling}, the 
attacker uploads the PDF polyglot to a vulnerable content hosting service. 
A server-side verification process will base its verification on the benign formats 
it expects to receive. The polyglot is designed to verify correctly as the benign format,
and the verification is likely to miss the malicious PDF components, as it is unaware of the alternate interpretation of the content.

@@

Listing~\ref{lst:xml-pdf} contains an example PDF document that uses XML external 
entities. The one-way method \emph{getURL} is used to communicate the 
information back to the attacker. Given the compact size of the example, it is useful for the syntax 
injection scenario in Section~\ref{sec:injection}, which require injection of 
small syntax fragments.

@@

\paragraph{Content smuggling}
\label{sec:smuggling-mitigation}
The current best-practice recommendation
on hosting user-supplied content 
is to serve the content from a sandboxed origin that is 
completely separate, as per SOP, and isolated from the sensitive services. 
These best-practices, provided by Google~\cite{Google:ContentHosting}, successfully prevents content smuggling 
attacks as the restrictions of the SOP prevents the content from accessing any sensitive 
resources in the origin of the web service.
